Compute Servers for Teaching Big Data

### 2025-01-28 paper.tex
rearrange

\subsection{Best option - Dedicated Support and Infrastructure}

@@

\subsection{Option 1 - Personal Physical Server}

@@

\subsection{Option 2 - Public Cloud}

@@

\subsection{Option 3 - Commercial Cloud}

@@

If it was easier to set up and run a server, then we believe that more instructors would be interested in teaching this kind of class.
For a lone instructor with no support, the barriers to entry are significant.
We would welcome a solution that provides this capability publicly.
It must have the following features:
\begin{enumerate}
\item \textbf{command line access} If this is present, then it should be possible to install and use all manner of command line software, including R, Python, and SQL.
\item \textbf{100 GB data storage} 
\item \textbf{free or low cost} Free for students is ideal, of course.
    If that's not possible, then the cost over the semester should not exceed that of a reasonably priced textbook.
\end{enumerate}
Based on our observations above, there are several other features that would be nice to have, and we list them here in order of preference.

>>>>

\subsection{Dedicated Support and Infrastructure}

@@

\subsection{Personal Physical Server}

@@

\subsection{Public Cloud}

@@

\subsection{Commercial Cloud}

@@

If it was easier to set up and run a server, then we believe that more instructors would be interested in teaching this kind of class.
For a lone instructor with no support, the barriers to entry are significant.
We would welcome a solution that provides this capability publicly.
It must have the following features:
\begin{enumerate}
\item \textbf{command line access} If this is present, then it should be possible to install and use all manner of command line software, including R, Python, and SQL.
\item \textbf{100 GB data storage} 
\item \textbf{free or low cost} Free for students is ideal, of course.
    If that's not possible, then the cost over the semester should not exceed that of a reasonably priced textbook.
\end{enumerate}
Based on our observations above, there are several other features that would be nice to have, and we list some of them here.
